Contextual Combinatorial Cascading Bandits

### 2015-12-25 experiment/experiment.tex
add proximity prove

\newcommand{\RR}{\mathbb{R}}
\newcommand{\cS}{\mathcal{S}}

@@

>>>>

\newcommand{\RR}{\mathbb{R}}
\newcommand{\cS}{\mathcal{S}}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

\subsection{Routing}

Let $G=(V,E=\{e_1,...,e_L\})$ be the topology representation of an ISP network, $G$ is then symmetric by it's definition. 
Considering the scinario where a package is sent from its source node to its destination, it's returned back to the source after trying to bypass an edge with high latency.
And the routing is failed if so, and the source will receive the routing history till the failing edge.
The agent is then motivated to assign an routing path, which can be recognized as an simple path in $G$ from the source node to the destination node, so as to avoid edges with high latency. 
Assume we have some sort of tell about the dynamics of the network conditions between the hosts, each being encoded in a $d$-dimentional vector, the network routing problem is to find the routing path least likely to involve an edge with high latency.
Denote $x_{i,t}$ be the vector associated with edge $e_i$, at time $t$, assume the corresponding latency is drawn from an exponential distribution with mean $1 - \theta_{\ast}^{\top}x_{t,i}$ independently,
and define the latency is high iff it's greater than a constant tolerance value $\tau$.
We formulate the network routing as an contextual combinatorial cascading problem.

Let $E=\{e_1,...,e_L\}$ be the set of arms, and $x_{i,t}$ be the context associated with arm $e_i$ at time $t$.
In order to send a package from $u_t$ to $v_t$,
the agent have to choose an superarm from $$S=\{A=(e_{k_1},...,e_{k_n}):e_{k_j}\in E, e_{k_1},...,e_{k_n} \text{is a simple path of } G \text{ from } u_t \text{ to } v_t\},$$
with the expected payoffs (opt out discount) $$E[r_A]=\Pi_{1\leq i\leq n(A)}(1-\exp(-\tau/(1-\theta_{\ast}^{\top}x_{k_i,t}))).$$
The agent finds $A_t$ by running shortest path algorithm on $G$ with weight $\hat{\theta}^{\top}x_{k_i,t}$ assigned to $e_i$, which yields $$A_t=\argmin_{Z\in S}\sum_{1\leq i\leq n(Z)}\hat{\theta}^{\top}x_{k_i,t}.$$
We have then $$\max_{A\in S}E[r_A]/E[r_{A_t}]\leq \alpha(\tau, d) = (1-e^{-\tau})^d/(1-e^{-\tau / d}).$$
Hence we can realize the $\alpha(\tau, d)$ oracle using shortest path algorithm.
After the agent choose the shortest path as the superarm, the reward and the first ever edge with high latency, if any, is feedbacked.
